|

### 2025-01-27 doc/paper.qmd
semi-strong market efficiency

Building on this foundation, the original study by @ball_how_2008 investigates the extent to which quarterly earnings announcements contribute new information to the market, assessing their role in shaping annual share price movements. By estimating the R² from regressions of annual stock returns on earnings announcement window returns, the paper quantifies the informativeness of earnings releases, finding that they account for only 1% to 2% of total annual volatility. This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights. Unlike traditional event studies that assume market efficiency, @ball_how_2008 allow for potential market mispricing by not imposing a unit slope restriction in their regressions, meaning that their approach can capture under- or overreaction to earnings announcements. They also emphasize that extending the event window beyond the earnings announcement period would shift the research focus from earnings “surprise” to broader financial reporting effects, such as its role in debt contracting and executive compensation. The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.

@@

@@

**Step 1: Pulling the Data and Managing the Database**  
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

>>>>

Building on this foundation, the original study by @ball_how_2008 investigates the extent to which quarterly earnings announcements contribute new information to the market, assessing their role in shaping annual share price movements. By estimating the R² from regressions of annual stock returns on earnings announcement window returns, the paper quantifies the informativeness of earnings releases, finding that they account for only 1% to 2% of total annual volatility. This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights. Their findings align with the semi-strong form of market efficiency, which suggests that stock prices already reflect all publicly available information, including prior signals about earnings. Unlike traditional event studies that assume market efficiency, @ball_how_2008 allow for potential market mispricing by not imposing a unit slope restriction in their regressions, meaning that their approach can capture under- or overreaction to earnings announcements. They also emphasize that extending the event window beyond the earnings announcement period would shift the research focus from earnings “surprise” to broader financial reporting effects, such as its role in debt contracting and executive compensation. The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.

@@

CRSP/COMPUSTAT MERGED database allows for concurrent database access to CRSP’s stock data and Compustat’s fundamental data.

@@

**Step 1: Pulling the Data and Managing the Databases**  
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.
